---
title: "Hospital Sungai Buloh PPS 2024"
description: |
  Data Manipulation and Analysis for Hospital Sungai Buloh, Point Prevalence Survey,(PPS) 2024.
author:
  - first_name: Adam 
    last_name: Jaafer, PharmD
    affiliation: Sungai Buloh Hospital
  - first_name: Izyana Munirah 
    last_name: Idham, MClinPharm
    affiliation: Sungai Buloh Hospital
  - first_name: Hannah
    last_name: Mahir, MClinPharm
    affiliation: Sungai Buloh Hospital
  - first_name: Fong
    last_name: Siew Li, BPharm
    affiliation: Sungai Buloh Hospital
date: "`r Sys.Date()`"

output: 
 distill::distill_article:
    toc: true
    code_folding: false
    self_contained: false
format:
  html:
    embed-resources: true
    toc: true
    toc-float: true
    toc-location: left
---

<!--------------- my typical setup ----------------->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# VARIABLES MANAGEMENT IN EXCEL

## Steps to Prepare Data in Excel before R wrangling (Macro available)

1.  Power query data from PPS in AMS folder (refer Power Query guide)
2.  Missing Data Management
    -   Remove ERROR, #REF! and #N/A using find and replace ALL
    -   Double check missing data cell
    -   DO NOT PUT NA during data entry
3.  Remove Duplicate patients
    -   Conditional formatting \> Highlight cell rules \> Duplicate values
    -   Sort by Date (oldest to newest)
    -   Remove latest entries (keep older entries)
    -   Readjust SORT column
4.  Save file as excel **workbook** named "HSGB_PPS" in PPS HSGB/Data Analysis/R folder
5.  Make sure in folder /excel/ contains 3 excel files:
    -   FINALPPSbyABX_202X.xlsx (file from previous year)
    -   traffic.xlsx
    -   Prevalence_analysis_202X.xlsx (file from previous year)

# DATA CLEANUP

## Load libraries & setup working directories and folders

```{r library}
pacman::p_load(
     rio,          # import function without /
     purrr,        # iteration
     tidyverse,    # data management and visualization
     writexl,      # write Excel file with multiple sheets
     readxl,        # import Excel with multiple sheets
     here,          # make calling folders 
     kableExtra,   #create awesome table in HTML
     lubridate,    # date manipulation
     reshape2,     # melt fucntion
     janitor,       # data cleaning
     forcats,      # data categorisation
     scales,       # data cleaning
     gtsummary,    # data presentation/table1
     ggplot2,       # dataviz
     glue          # glue syntax
)

#set working directories
setwd(here::here())
getwd()

# Create the output folder if it doesn't exist
if (!dir.exists("table")) dir.create("table") #to store tables
if (!dir.exists("image")) dir.create("image") #to store images

```

## Load and Clean PPS Current Year data into R

```{r load main data}

library(readxl)
PPS <- read_excel("HSGB_PPS.xlsx", 
    sheet = "Patient & Abx Data ") #select excel workbook and sheet

#Remove Line breaks, SPACE, symbols such as '(', ')', '\~?', '.', and '/'
    #-   replace with underscore

PPS <- clean_names(PPS) %>% #clean data (remove whitespace, duplicate headers, unwanted characters etc)
 rowid_to_column("SORT") #add row_ID in sequence
  
write_xlsx(PPS, "excel/PPS_raw.xlsx") #double check with excel

#extracting LATEST YEAR
str(PPS$audit_date)
latest_year <- year(PPS$audit_date[1])
second_latest_year <- latest_year - 1
nrow_PPS <- nrow(PPS)
```

## Updating Data for prevalance analysis & Load into R

Additional excel sheet needs to be updated from previous PPS

Prevalence_analysis - column = year, antibiotics_prescribed (yes/no), compliance - to be updated using prevalence data of total patient in ward and patient on antibiotics - by pt

```{r updating prevalence sheet}

pt_on_abx <- read_excel("HSGB_PPS.xlsx", sheet = "Ward Data", range = "J4", col_names = FALSE) #extrating pt on abx from ward_data sheet (from cell J4 = number of pt on ABX)
pt_not_abx <- read_excel("HSGB_PPS.xlsx", sheet = "Ward Data", range = "K4", col_names = FALSE) #extrating pt not on abx from ward_data sheet (from cell K4 = number of pt NOT on ABX)

no_pt_on_abx <- pt_on_abx[[1,1]] #assign var as value
no_pt_not_abx <- pt_not_abx[[1,1]] #assign var as value

if (nrow_PPS != no_pt_on_abx) {
  stop("Mismatch!")
}

# Sample data (patients with prescribed antibiotics and not prescribed)
df_prev <- tibble(
  id = 1:(no_pt_on_abx + no_pt_not_abx),
  Abx_prescribed = c(rep("Yes", no_pt_on_abx), rep("No", no_pt_not_abx)),  #df of prevalence abx prescribed of that year
  Year = latest_year) #year need to change!

#create df of compliance to guideline to be merged later
df_prev1 <- PPS %>% 
  mutate(
    Compliance = case_when(
      overall_compliance_to_antibiotic_guideline == "Compliant to guidelines" ~ "yes",
      overall_compliance_to_antibiotic_guideline == "Not-compliant to guidelines" ~ "no",
      overall_compliance_to_antibiotic_guideline == "NA" ~ "na",  # Assuming 'na' is a string, not actual NA
      is.na(overall_compliance_to_antibiotic_guideline) ~ "NA",  # Handling actual NA values
      TRUE ~ as.character(overall_compliance_to_antibiotic_guideline)  # Leave other values unchanged
    )
  ) %>%
  select(Compliance)

#dummy df for cell value of compliance
compliance_counts <- df_prev1 %>%
  count(Compliance) %>%
  spread(Compliance, n, fill = 0)

# Assigning variables for compliance counts from the summarized dataset
compliance_yes_count <- compliance_counts$yes
compliance_no_count <- compliance_counts$no
compliance_unknown_count <- compliance_counts$na
compliance_notavail_count <- pt_not_abx[[1,1]]

#validation 
total_compliance_needed <- sum(df_prev$Abx_prescribed == "Yes")
total_compliance_provided <- compliance_yes_count + compliance_no_count + compliance_unknown_count
total <- compliance_yes_count + compliance_no_count + compliance_unknown_count + compliance_notavail_count

if (total_compliance_needed != total_compliance_provided) {
  stop("Mismatch between number of 'yes' abx_prescribed and total compliance counts.")
}

compliance_vector <- sample(
  c(rep("yes", compliance_yes_count), 
    rep("no", compliance_no_count), 
    rep("na", compliance_unknown_count))
)

length(compliance_vector)
# Adjusting the compliance distribution based on counts from the summary
df_prev2 <- df_prev %>%
  filter(Abx_prescribed == "Yes") %>%
  mutate(Compliance = if_else(
    Abx_prescribed == "Yes", 
    compliance_vector,               # Exact match for 'yes' rows
    "NotAvail"          # Default NA for any missing data
  ))

new_prev_analysis <- df_prev %>%
  left_join(df_prev2, suffix = c("", ".new")) %>%
  mutate(Compliance = ifelse(is.na(Compliance), "NotAvail", Compliance)) %>%
  mutate(across(where(is.character), tolower)) %>%
  select(Year, Abx_prescribed, Compliance)

#NEXT STEP IS TO COMBINE CURRENT DATA TO EXISTING SPREADSHEET

#load available prevalence_analysis.xlsx
existing_prev_analysis <- read_excel(paste0("excel/Prevalence_analysis_", second_latest_year, ".xlsx"))

#validation of rows in current prevalence sheet
new_rows <- anti_join(new_prev_analysis, existing_prev_analysis, by = c("Year", "Abx_prescribed", "Compliance"))

#join existing + new prevalence analysis into one spreadsheet
combined_prev_analysis <- bind_rows(existing_prev_analysis, new_rows)

#save to excel sheet
write_xlsx(combined_prev_analysis, paste0("excel/Prevalence_analysis_", latest_year, ".xlsx"))
```
```{r remove variables}
rm(pt_on_abx, pt_not_abx, df_prev,df_prev1, df_prev2, compliance_counts, compliance_vector, new_prev_analysis, existing_prev_analysis, new_rows)

rm(nrow_PPS,total_compliance_needed, total_compliance_provided, compliance_no_count, compliance_notavail_count, compliance_unknown_count, compliance_yes_count)
```

## View Data frame

```{r data, R.options = list(width = 100)}
glimpse(PPS)
```

```{r data2, R.options = list(width = 100), results='hide'}

options(width = 60)
skimr::skim(PPS) %>%
  kable() %>%
  kable_paper(bootstrap_options = "striped", full_width = F, position = "center")
```

# PIVOT LONGER USING MELT

## Manipulate PPS DATA from wide to long - using reshape2 library

Separate melt for each columns from HSGB_PPS excel sheet

```{r melting antibiotic name}
options(width = 60)
melt_abxname <-
  PPS %>% 
  select(pt_reg_no, #control
         SORT, #control
         discipline, #control
         antibiotic_1_name, #will be melted
         antibiotic_2_name, #will be melted
         antibiotic_3_name, #will be melted
         antibiotic_4_name) %>% #will be melted
  melt(id=c("pt_reg_no" ,"SORT","discipline")) %>% #melt data stratify by pt reg no and SORT
  arrange(SORT) %>% #re arrange based on SBnumber
  filter(!is.na(value)) %>% #filter out NA in value column
  dplyr::rename(SBNUMBER = pt_reg_no, ABX1 = variable, ABX_NAME = value) %>% #rename column names
  select(-c(ABX1)) #remove column ABX1

kable(head(melt_abxname))
```

```{r melt antibiotic indication}
options(width = 60)
melt_indication <-
  PPS %>% 
  select(pt_reg_no, #control
         SORT, #control
         antibiotic_1_indication, #will be melted
         antibiotic_2_indication, #will be melted
         antibiotic_3_indication, #will be melted
         antibiotic_4_indication) %>% #will be melted
  melt(id=c("pt_reg_no","SORT")) %>% #melt data stratify by pt reg no and SORT
  arrange(SORT) %>% #re arrange based on SBnumber
  filter(!is.na(value)) %>% #filter out NA in value column
  dplyr::rename(SBNUMBER = pt_reg_no,
         ABX1 = variable,
         INDICATION = value) %>% #rename column names
  select(-c(ABX1)) #remove column ABX1

kable(head(melt_indication))
```

```{r melt indication by  group}
options(width = 60)
melt_diseasegroup <-
  PPS %>% 
  select(pt_reg_no, #control
         SORT, #control
         antibiotic_1_infection_disease_group_by_system, #will be melted
         antibiotic_2_infection_disease_group_by_system, #will be melted
         antibiotic_3_infection_disease_group_by_system, #will be melted
         antibiotic_4_infection_disease_group_by_system) %>% #will be melted
  melt(id=c("pt_reg_no","SORT")) %>% #melt data stratify by pt reg no and SORT
  arrange(SORT) %>% #re arrange based on SBnumber
  filter(!is.na(value)) %>% #filter out NA in value column
  dplyr::rename(SBNUMBER = pt_reg_no,
         ABX1 = variable,
         IND_DIS_GROUP = value) %>% #rename column names
  select(-c(ABX1)) #remove column ABX1

kable(head(melt_diseasegroup))
```

```{r melt indication type}
options(width = 60)
melt_typeind <-
  PPS %>% 
  select(pt_reg_no, #control
         SORT, #control
         antibiotic_1_infection_disease_type, #will be melted
         antibiotic_2_infection_disease_type, #will be melted
         antibiotic_3_infection_disease_type, #will be melted
         antibiotic_4_infection_disease_type) %>% #will be melted
  melt(id=c("pt_reg_no" , "SORT")) %>% #melt data stratify by pt reg no and SORT
  arrange(SORT) %>% #re arrange based on SBnumber
  filter(!is.na(value)) %>% #filter out NA in value column
  dplyr::rename(SBNUMBER = pt_reg_no,
         ABX1 = variable,
         TYPE_INDICATION = value) %>% #rename column names
  select(-c(ABX1)) #remove column ABX1

kable(head(melt_typeind))
```

```{r melt category}
options(width = 60)
melt_category <-
  PPS %>% 
  select(pt_reg_no, #control
         SORT, #control
         antibiotic_1_indication_category, #will be melted
         antibiotic_2_indication_category, #will be melted
         antibiotic_3_indication_category, #will be melted
         antibiotic_4_indication_category) %>% #will be melted
  melt(id=c("pt_reg_no" , "SORT")) %>% #melt data stratify by pt reg no and SORT
  arrange(SORT) %>% #re arrange based on SBnumber
  filter(!is.na(value)) %>% #filter out NA in value column 
  dplyr::rename(SBNUMBER = pt_reg_no,
         ABX1 = variable,
         CATEGORY = value) %>% #rename column names
  select(-c(ABX1)) #remove column ABX1

kable(head(melt_category))

```

```{r melt indication documented}
options(width = 60)
melt_inddocumented <-
  PPS %>% 
  select(pt_reg_no, #control
         SORT, #control
         antibiotic_1_indication_documented_within_24_h, #will be melted
         antibiotic_2_indication_documented_within_24_h, #will be melted
         antibiotic_3_indication_documented_within_24_h, #will be melted
         antibiotic_4_indication_documented_within_24_h) %>% #will be melted
  melt(id=c("pt_reg_no" , "SORT")) %>% #melt data stratify by pt reg no and SORT
  arrange(SORT) %>% #re arrange based on SBnumber
  filter(!is.na(value)) %>% #filter out NA in value column 
  dplyr::rename(SBNUMBER = pt_reg_no,
         ABX1 = variable,
         DOCUMENTED = value) %>% #rename column names
  select(-c(ABX1)) #remove column ABX1

kable(head(melt_inddocumented))
```

```{r melt compliance to guideline}
options(width = 60)
melt_compliance <-
  PPS %>% 
  select(pt_reg_no, #control
         SORT, #control
         antibiotic_1_compliance_to_guideline, #will be melted
         antibiotic_2_compliance_to_guideline, #will be melted
         antibiotic_3_compliance_to_guideline, #will be melted
         antibiotic_4_compliance_to_guideline) %>% #will be melted
  melt(id=c("pt_reg_no" , "SORT")) %>% #melt data stratify by pt reg no and SORT
  arrange(SORT) %>% #re arrange based on SBnumber
  filter(!is.na(value)) %>% #filter out NA in value column 
  dplyr::rename(SBNUMBER = pt_reg_no,
         ABX1 = variable,
         COMPLIANCE = value) %>% #rename column names
  select(-c(ABX1)) #remove column ABX1

kable(head(melt_compliance))
```

## Merge multiple dataframes initially melted

```{r merge multiple dataframes}
options(width = 60)

final_joined <-
  bind_cols(melt_abxname, 
            melt_category$CATEGORY, 
            melt_indication$INDICATION, 
            melt_typeind$TYPE_INDICATION,
            melt_diseasegroup$IND_DIS_GROUP,
            melt_inddocumented$DOCUMENTED,
            melt_compliance$COMPLIANCE) #joining multiple df by column (match row by position)

colnames(final_joined) <- 
  c('SBNUMBER',
    'SORT',
    'DISCIPLINE',
    'ABX_NAME', 
    'CATEGORY', 
    'INDICATION', 
    'TYPE_IND',
    'DISEASE_GROUP',
    'INDICATION_DOCUMENTED',
    'COMPLIANCE') #rename column names


head(final_joined) %>%
  kable() %>%
  kable_paper(bootstrap_options = "striped", full_width = F, position = "center")

skimr::skim(final_joined)

final_joined <- final_joined %>%
  mutate(ABX_NAME = str_replace_all(ABX_NAME, "Benzylpenicillin \\(Penicillin G\\)", "Benzylpenicillin")) %>% #Change benzylpenicillin to match with traffic light
  mutate(ABX_NAME = str_replace_all(ABX_NAME, "Polymyxin E \\(Colistin\\)", "Colistin")) #Change colistin to match with traffic light
```

# COMBINE OLD & NEW DATA

## Assign traffic_light to ABX

```{r matching traffic light dataset with final_joined}

#create datasets of unique antibiotic list
unique_ABX <- final_joined %>%
  distinct(ABX_NAME) %>% 
  arrange(ABX_NAME)

#load traffic light excel
traffic <- read_excel("excel/traffic.xlsx")

#full_join both melted data with traffic light & writexl
ABX_data <- left_join(final_joined, traffic, by = "ABX_NAME")


skimr::skim(ABX_data)

#reorder columns and replace all caps abx name & ind_category in column ABX_NAME & CATEGORY
# factorized traffic lights and indication category
ABX_data <- ABX_data %>%
  select(SBNUMBER, ABX_NAME, TF, everything()) %>% 
  select(-SORT) %>%
  mutate(ABX_NAME = tolower(ABX_NAME)) %>%
  mutate(CATEGORY = tolower(CATEGORY)) %>%
  mutate(INDICATION_DOCUMENTED = tolower(INDICATION_DOCUMENTED)) %>%
  mutate(TF = factor(TF, levels = c("green", "yellow", "red"))) %>% #change order of traffic light system from green, yellow and red
  mutate(CATEGORY = factor(CATEGORY, levels = c("definitive therapy", "empirical therapy", "surgical prophylaxis", "non-surgical prophylaxis"))) %>%
  #change order of indication category
  mutate(INDICATION_DOCUMENTED = factor(INDICATION_DOCUMENTED, levels = c("yes", "no"))) %>%
  mutate(Year = latest_year) #add latest  year

#save to excel file
write_xlsx(ABX_data, paste0("excel/ABXDATA_", latest_year, ".xlsx"))

#double check for missing data/input error
skimr::skim(ABX_data)
ABX_n <- nrow(ABX_data)

```
##verify data and remove unused df

```{r verify data factors}

# Define the columns for which you want to find unique values
columns <- c("ABX_NAME", "CATEGORY", "TYPE_IND", "DISEASE_GROUP", "INDICATION_DOCUMENTED","COMPLIANCE")

# Loop through each column and find unique values
for (col in columns) {
  unique_data <- ABX_data %>%
  distinct(!!sym(col)) %>% 
  arrange(!!sym(col))
  
  # Store the unique data in a variable with the column name
  assign(paste0("unique_", col), unique_data)
}

```

```{r remove df1}

rm(list = ls(pattern = "unique_"))
rm(list = ls(pattern = "melt_"))
rm(final_joined, traffic,col, columns)
```

## Summarizing data for graphs

```{r Summarized data}

#group by abx names

GRAPH_TOTAL_ABX <-
ABX_data %>%
  group_by(ABX_NAME) %>%
  summarize(count = n()) %>%
  arrange(desc(count)) %>%
  mutate(percentage =count/sum(count)) %>%
  mutate(percentage =round(percentage, 3)) 

#group by empirical

GRAPH_TOTAL_ABX_EMPIRICAL <-
ABX_data %>%
  group_by(ABX_NAME) %>%
  filter(CATEGORY == "empirical therapy") %>%
  summarize(count = n()) %>%
  arrange(desc(count)) %>%
  mutate(percentage =count/sum(count))%>%
  mutate(percentage =round(percentage, 3))

#group by definitive therapy

GRAPH_TOTAL_ABX_DEFINITIVE <-
ABX_data %>%
  group_by(ABX_NAME) %>%
  filter(CATEGORY == "definitive therapy") %>%
  summarize(count = n()) %>%
  arrange(desc(count)) %>%
  mutate(percentage =count/sum(count))%>%
  mutate(percentage =round(percentage, 3))

#group by surgical prophylaxis

GRAPH_TOTAL_ABX_SURGICAL <-
ABX_data %>%
  group_by(ABX_NAME) %>%
  filter(CATEGORY == "surgical prophylaxis") %>%
  summarize(count = n()) %>%
  arrange(desc(count)) %>%
  mutate(percentage =count/sum(count))%>%
  mutate(percentage =round(percentage, 3))

#group by indications

GRAPH_TOTAL_IND <- ABX_data %>%
  mutate(TYPE_IND = str_replace_all(TYPE_IND, c(
    "Hospital-acquired Pneumonia \\(HAP/VAP\\)" = "HAP/VAP",
    "Orthopaedic Trauma-related Infections \\(.*?\\)" = "Orthopaedic Trauma Infections",
    "Others \\(Indication not in guideline\\)" = "Indication NOT in Guideline",
    "Respiratory Infections" = "Respi Infections (Paeds)",
    "Surgical Infection - Appendicitis \\(.*?\\)" = "Appendix-related Infections",
    "Bed Sore / Pressure Sore / Decubitus Ulcer" = "Pressure sores/Ulcers"
  ))) %>%
  group_by(TYPE_IND) %>%
  summarize(count = n()) %>%
  arrange(desc(count)) %>%
  mutate(percentage =count/sum(count))%>%
  mutate(percentage =round(percentage, 3)) 
  sum(GRAPH_TOTAL_IND$count)

#guideline compliance
GRAPH_TOTAL_COMPLIANCE <- 
  ABX_data %>%
  group_by(DISCIPLINE) %>%
  filter(COMPLIANCE == "Non-compliance to guidelines") %>%
  summarize(count = n()) %>%
  arrange(desc(count)) %>%
  mutate(percentage =count/sum(count))%>%
  mutate(percentage =round(percentage, 3))
  
```

## Adding traffic-lights

```{r add TF }

#all abx
GRAPH_ALL_ABX_TF <-
  ABX_data %>%
  group_by(ABX_NAME, TF) %>%
  summarize(count = n()) %>%
  arrange(desc(count)) %>%
  select(ABX_NAME, TF) %>%
  right_join(GRAPH_TOTAL_ABX, by ="ABX_NAME")
sum(GRAPH_ALL_ABX_TF$count)

#empirical therapy

GRAPH_empirical_TF <-
  ABX_data %>%
  filter(CATEGORY == "empirical therapy") %>%
  group_by(ABX_NAME, TF) %>%
  summarize(count = n()) %>%
  arrange(desc(count)) %>%
  select(ABX_NAME, TF) %>%
  right_join(GRAPH_TOTAL_ABX_EMPIRICAL, by ="ABX_NAME")

  #validation of sum 
  if (sum(GRAPH_empirical_TF$count) != sum(GRAPH_TOTAL_ABX_EMPIRICAL$count)) {
      stop("Mismatch!")}

#definitive therapy
GRAPH_definitive_TF <-
  ABX_data %>%
  filter(CATEGORY == "definitive therapy") %>%
  group_by(ABX_NAME, TF) %>%
  summarize(count = n()) %>%
  arrange(desc(count)) %>%
  select(ABX_NAME, TF) %>%
  right_join(GRAPH_TOTAL_ABX_DEFINITIVE, by ="ABX_NAME")

  #validation of sum 
  if (sum(GRAPH_definitive_TF$count) != sum(GRAPH_TOTAL_ABX_DEFINITIVE$count)) {
    stop("Mismatch!")}

#surgical prophylaxis

GRAPH_surgicalprophylaxis_TF <-
  ABX_data %>%
  filter(CATEGORY == "surgical prophylaxis") %>%
  group_by(ABX_NAME, TF) %>%
  summarize(count = n()) %>%
  arrange(desc(count)) %>%
  select(ABX_NAME, TF) %>%
  right_join(GRAPH_TOTAL_ABX_SURGICAL, by ="ABX_NAME")

  #validation of sum 
  if (sum(GRAPH_surgicalprophylaxis_TF$count) != sum(GRAPH_TOTAL_ABX_SURGICAL$count)) {
     stop("Mismatch!")}

#compliance by discipline

GRAPH_compliancevsdiscipline <-
  ABX_data %>%
  filter(COMPLIANCE == "Non-compliance to guidelines") %>%
  group_by(DISCIPLINE, COMPLIANCE) %>%
  summarize(count = n()) %>%
  arrange(desc(count)) %>%
  select(DISCIPLINE, COMPLIANCE) %>%
  right_join(GRAPH_TOTAL_COMPLIANCE, by ="DISCIPLINE")


```

```{r add category}

GRAPH_CAT1 <-
  ABX_data %>%
  group_by(CATEGORY, ABX_NAME) %>%
  summarize(count = n()) %>%
  arrange(desc(CATEGORY)) %>% 
  mutate(percentage =count/sum(count)) %>%
  mutate(percentage =round(percentage, 3))

GRAPH_CAT2 <-
  GRAPH_CAT1 %>%
  group_by(ABX_NAME, CATEGORY) %>%
  summarise(count = sum(count)) %>%  
  mutate(percent = count/sum(count))

GRAPH_JOINED_CAT<- 
left_join(GRAPH_TOTAL_ABX, GRAPH_CAT1, by="ABX_NAME")
```

# DATA VISUALIZATION

## Total Antibiotic Prescribed in PPS

```{r ggplot total abx data}

GRAPH_ALL_ABX_TF %>%
  mutate(ABX_NAME = stringr::str_to_title(ABX_NAME)) %>% #capitalize each abx names
  ggplot(aes(x = reorder(ABX_NAME,count), y = percentage, fill = TF)) + 
  geom_col(color = "black") + 
  scale_fill_manual(values = c("#00FF00","#FCE205","red")) +
  geom_vline(xintercept = 22.5, linetype="dashed", #adjust cutoff
                color = "blue", size=0.5) +
  coord_flip() + 
  geom_text(aes(label = count), position = position_stack(vjust = 0.5), size = 3) + 
  annotate("text", x=23, y=0.15, label="Top 10", angle=0, size = 3) +
  labs(title = glue("Total ABX prescribed (n = {ABX_n})"),
       x = "",
       y = "",
       fill = "Restriction Category") +
  scale_y_continuous(labels = percent_format(),
                     ) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        panel.background = element_rect(fill = "white"),
        axis.text = element_text(size = 7),
        legend.text = element_text(size = 7),
        legend.title = element_text(size = 7),
        axis.text.y = element_text(size = 8, face = "bold"))
  
  ggsave("TOTALABX.tiff", units="in", width=10, height=5, dpi=300, compression = 'lzw', path = "image")

```

## Top 10 Antibiotic Prescribed

```{r ggplot top 10 abx data}

GRAPH_ALL_ABX_TF %>% 
  ungroup() %>% 
  mutate(ABX_NAME = stringr::str_to_title(ABX_NAME)) %>% #capitalize each abx names
  top_n(10, count) %>%
  ggplot(aes(x = reorder(ABX_NAME,count), y = percentage, fill = TF)) + 
  geom_col(color = "black") + 
  scale_fill_manual(values = c("#00FF00","#FCE205","red")) +
  geom_vline(xintercept = 20.5, linetype="dashed", 
                color = "blue", size=0.5) +
  coord_flip() + 
  geom_text(aes(label = paste0(count, '(', percentage*100,'%)')), position = position_stack(vjust = 0.5), size = 4) +
  labs(title = "Top 10 Antibiotics prescribed",
       x = "",
       y = "",
       fill = "Restriction Category") +
  scale_y_continuous(labels = percent_format()) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        panel.background = element_rect(fill = "white"),
        axis.text = element_text(size = 7),
        legend.text = element_text(size = 7),
        legend.title = element_text(size = 7),
        axis.text.y = element_text(size = 16, face = "bold"))
  
  ggsave("TOP10ABX.tiff", units="in", width=10, height=5, dpi=300, compression = 'lzw', path = "image")

```

## Top 10 Empirical Antibiotics

```{r ggplot abx data empirical}
  #
GRAPH_empirical_TF%>%
  ungroup() %>% 
  mutate(ABX_NAME = stringr::str_to_title(ABX_NAME)) %>% #capitalize each abx names
  top_n(n=10, count) %>%
  ggplot(aes(x = reorder(ABX_NAME,count), y = percentage, fill = TF)) + 
  geom_col(color = "black") + 
  scale_fill_manual(values = c("#00FF00","#FCE205","red")) +
  geom_vline(xintercept = 20.5, linetype="dashed", 
                color = "blue", size=0.5) +
  coord_flip() + 
  geom_text(aes(label = paste0(count, '(', percentage*100,'%)')), position = position_stack(vjust = 0.5), size = 4) +
  labs(title = "Top 10 Empirical Antibiotics",
       x = "",
       y = "",
       fill = "Restriction Category") +
  scale_y_continuous(labels = percent_format()) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        panel.background = element_rect(fill = "white"),
        axis.text = element_text(size = 7),
        legend.text = element_text(size = 7),
        legend.title = element_text(size = 7),
        axis.text.y = element_text(size = 16))

  ggsave("TOP10EMPABX.tiff", units="in", width=10, height=5, dpi=300, compression = 'lzw', path = "image")

```

## Definitve Antibiotics

```{r ggplot abx data definitive}

GRAPH_definitive_TF%>%
  ungroup() %>% 
  mutate(ABX_NAME = stringr::str_to_title(ABX_NAME)) %>% #capitalize each abx names
  top_n(n=10, count) %>%
  ggplot(aes(x = reorder(ABX_NAME,count), y = percentage, fill = TF)) + 
  geom_col(color = "black") + 
  scale_fill_manual(values = c("#00FF00","#FCE205","red")) +
  geom_vline(xintercept = 20.5, linetype="dashed", 
                color = "blue", size=0.5) +
  coord_flip() + 
  geom_text(aes(label = paste0(count, '(', percentage*100,'%)')), position = position_stack(vjust = 0.5), size = 4) +
  labs(title = "Top 10 Definitive Antibiotics",
       x = "",
       y = "",
       fill = "Restriction Category") +
  scale_y_continuous(labels = percent_format()) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        panel.background = element_rect(fill = "white"),
        axis.text = element_text(size = 7),
        legend.text = element_text(size = 7),
        legend.title = element_text(size = 7),
        axis.text.y = element_text(size = 16, face = "bold"))

ggsave("TOP10DEFABX.tiff", units="in", width=10, height=5, dpi=300, compression = 'lzw', path = "image")

```

## Surgical Prophylaxis

```{r surgical prop abx}

GRAPH_surgicalprophylaxis_TF %>%
  mutate(ABX_NAME = stringr::str_to_title(ABX_NAME)) %>% #capitalize each abx names
  ggplot(aes(x = reorder(ABX_NAME,count), y = percentage, fill = TF)) + 
  geom_col(color = "black") + 
  scale_fill_manual(values = c("#00FF00","#FCE205","red")) +
    geom_vline(xintercept = 20.5, linetype="dashed", 
                color = "blue", size=0.5) +
  coord_flip() + 
  geom_text(aes(label = paste0(count, '(', percentage*100,'%)')), position = position_stack(vjust = 0.5), size = 4) +
  labs(title = "Surgical Prophylaxis Antibiotics",
       x = "",
       y = "",
       fill = "Restriction Category") +
  scale_y_continuous(labels = percent_format()) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        panel.background = element_rect(fill = "white"),
        axis.text = element_text(size = 7),
        legend.text = element_text(size = 7),
        legend.title = element_text(size = 7),
        axis.text.y = element_text(size = 16, face = "bold"))


  ggsave("TOP10SURG.tiff", units="in", width=10, height=5, dpi=300, compression = 'lzw', path = "image")
```

## Top Antibiotic Prescriber PPS

```{r discipline}

GRAPH_Discpline1 <-
ABX_data %>% 
  mutate(DISCIPLINE = str_replace(DISCIPLINE, "COVID General Adults", "Infectious Disease")) %>%
  group_by(DISCIPLINE) %>%
  summarise(count = n()) %>%
  arrange(desc(count)) %>%
  mutate(percentage =count/sum(count))
sum(GRAPH_Discpline1$count) 
    
GRAPH_Discpline1 %>%
  ggplot(aes(x = reorder(DISCIPLINE,count), y = percentage, fill = DISCIPLINE)) + 
  geom_col(color = "black") + 
  scale_x_discrete(labels = ~ ifelse(.x == "Infectious Disease", paste0(.x, "*"), .x)) +
  coord_flip() + 
  geom_text(aes(label = count), position = position_stack(vjust = 0.5)) +
  labs(title = "Top Antibiotic prescriber",
       x = "",
       y = "") +
  scale_y_continuous(labels = percent_format()) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        panel.background = element_rect(fill = "white"),
        legend.position = "none",
        axis.text = element_text(size = 7),
        legend.text = element_text(size = 7),
        legend.title = element_text(size = 7),
        axis.text.y = element_text(size = 12, face = "bold"),
        plot.caption = element_text(hjust = 1))
  ggsave("TOPPRESCRIBER.tiff", units="in", width=10, height=5, dpi=300, compression = 'lzw', path = "image")

  
```

## Top 10 Antibiotic by Indication Category

```{r ggplot top 10 abx data by cat}

GRAPH_CAT1%>% 
  mutate(CATEGORY = factor(CATEGORY, levels = c("non-surgical prophylaxis", "surgical prophylaxis","definitive therapy","empirical therapy"))) %>%
  semi_join(
    ABX_data %>%
      count(ABX_NAME, sort = TRUE) %>%
      slice_head(n = 10),
    by = "ABX_NAME"
  ) %>%
  mutate(ABX_NAME = stringr::str_to_title(ABX_NAME)) %>% #capitalize each abx names
    
  ggplot(aes(x = fct_reorder(ABX_NAME, count, sum), y = count, fill = CATEGORY)) + 
  geom_col(color = "black") +
  scale_fill_manual(values = c("#C3B1E1","#7EC8E3","#76B947","#E7625F")) +
  #geom_vline(xintercept = 20.5, linetype="dashed", 
                #color = "blue", size=0.5) +
  coord_flip() + 
  geom_text(aes(label = ifelse(count >= 2, count,"")), position = position_stack(vjust = 0.5), size = 4) +
  labs(title = "Top 10 Antibiotics prescribed",
       x = "",
       y = "",
       fill = "Category") +
 theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
       panel.background = element_rect(fill = "white"),
       axis.text = element_text(size = 7),
       legend.text = element_text(size = 7),
       legend.title = element_text(size = 7),
       axis.text.y = element_text(size = 12, face = "bold")) 
       
ggsave("TOP10ABX2.tiff", units="in", width=10, height=5, dpi=300, compression = 'lzw', path = "image")

```

## Top 10 Antibiotic by indication category (visualize by %)

```{r top10abxbyIND_Cat}

GRAPH_CAT2 %>%
  mutate(CATEGORY = factor(CATEGORY, levels = c("non-surgical prophylaxis", "surgical prophylaxis","definitive therapy","empirical therapy"))) %>%
  semi_join(
    ABX_data %>%
      count(ABX_NAME, sort = TRUE) %>%
      slice_head(n = 10),
    by = "ABX_NAME"
  ) %>%
  mutate(ABX_NAME = stringr::str_to_title(ABX_NAME)) %>% #capitalize each abx names
  
ggplot(aes(x= fct_reorder(ABX_NAME, count, sum), y = percent, fill = CATEGORY)) + 
  geom_col(color = "black") +
  scale_fill_manual(values = c("#C3B1E1","#7EC8E3","#76B947","#E7625F")) +
  coord_flip() + 
  geom_text(aes(label=ifelse(percent >= 0.14, paste0(count, " (",sprintf("%.0f", percent*100),"%",")"),"")), position = position_stack(vjust = 0.5), size = 4) +
  labs(title = "Top 10 Antibiotics prescribed",
       x = "",
       y = "",
       fill = "Category") +
 theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
       panel.background = element_rect(fill = "white"),
       axis.text = element_text(size = 7),
       legend.text = element_text(size = 7),
       legend.title = element_text(size = 7),
       axis.text.y = element_text(size = 12, face = "bold")) +
 scale_y_continuous(labels = percent_format()) +
 scale_x_discrete(position = "bottom")

ggsave("TOP10ABX3.tiff", units="in", width=10, height=5, dpi=300, compression = 'lzw', path = "image")

```

## Top 10 Indication of antibiotic prescription

```{r}

GRAPH_TOTAL_IND %>%
  head(10) %>%
  ggplot(aes(x = reorder(TYPE_IND,count), y = percentage)) + 
  geom_col(aes(fill = count), stat = "identity") + 
  scale_fill_gradient2(low = "white", 
                       high = "red") + 
  scale_x_discrete(label = function(x) str_wrap(x, width = 20)) +
  coord_flip() + 
  geom_text(aes(label = paste0(count, '(', percentage*100,'%)')), position = position_stack(vjust = 0.5), size = 4) +
  labs(title = glue("Total ABX prescribed (n = {ABX_n})"),
       x = "",
       y = "") +
  scale_y_continuous(labels = percent_format()) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        panel.background = element_rect(fill = "white"),
        legend.position = "none",
        axis.text = element_text(size = 7),
        legend.text = element_text(size = 7),
        legend.title = element_text(size = 7),
        plot.margin = unit(c(0, 0, 0, 0), "in"),
        axis.text.y = element_text(size = 10,
                                   face = "bold"))
ggsave("TOPIND.tiff", units="in", width=10, height=5, dpi=300, compression = 'lzw', path = "image")

```

## Compliance rate by prescriber (graph)

```{r compliance by prescriber per abx}

GRAPH_compliancevsdiscipline %>%
  ggplot(aes(x = reorder(DISCIPLINE,count), y = percentage, fill = DISCIPLINE)) + 
  geom_col(color = "black") + 
  scale_x_discrete(labels = ~ ifelse(.x == "Infectious Disease", paste0(.x, "*"), .x)) +
  coord_flip() + 
  geom_text(aes(label = count), position = position_stack(vjust = 0.5)) +
  labs(title = "NON COMPLIANCE BY DISCIPLINE (BY ABX)",
       x = "",
       y = "") +
  scale_y_continuous(labels = percent_format()) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        panel.background = element_rect(fill = "white"),
        legend.position = "none",
        axis.text = element_text(size = 7),
        legend.text = element_text(size = 7),
        legend.title = element_text(size = 7),
        axis.text.y = element_text(size = 12, face = "bold"),
        plot.caption = element_text(hjust = 1))
  ggsave("TOPNONCOMPLIANCE.tiff", units="in", width=10, height=5, dpi=300, compression = 'lzw', path = "image")
 
```

## Compliance rate by prescriber (graph)

```{r compliance by prescriber by patient}

GRAPH_TOTAL_COMPLIANCE_PT <- 
  PPS %>%
  group_by(discipline) %>%
  filter(overall_compliance_to_antibiotic_guideline == "Not-compliant to guidelines") %>%
  summarize(count = n()) %>%
  arrange(desc(count)) %>%
  mutate(percentage =count/sum(count))%>%
  mutate(percentage =round(percentage, 3))

GRAPH_compliancebypatient <-
  PPS %>%
  filter(overall_compliance_to_antibiotic_guideline == "Not-compliant to guidelines") %>%
  group_by(discipline, overall_compliance_to_antibiotic_guideline) %>%
  summarize(count = n()) %>%
  arrange(desc(count)) %>%
  select(discipline, overall_compliance_to_antibiotic_guideline) %>%
  right_join(GRAPH_TOTAL_COMPLIANCE_PT, by ="discipline")

GRAPH_compliancebypatient %>%
  ggplot(aes(x = reorder(discipline,count), y = percentage, fill = discipline)) + 
  geom_col(color = "black") + 
  scale_x_discrete(labels = ~ ifelse(.x == "Infectious Disease", paste0(.x, "*"), .x)) +
  coord_flip() + 
  geom_text(aes(label = count), position = position_stack(vjust = 0.5)) +
  labs(title = "NON COMPLIANCE BY DISCIPLINE (BY PT)",
       x = "",
       y = "") +
  scale_y_continuous(labels = percent_format()) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        panel.background = element_rect(fill = "white"),
        legend.position = "none",
        axis.text = element_text(size = 7),
        legend.text = element_text(size = 7),
        legend.title = element_text(size = 7),
        axis.text.y = element_text(size = 12, face = "bold"),
        plot.caption = element_text(hjust = 1))
  ggsave("TOPNONCOMPLIANCEBYPT.tiff", units="in", width=10, height=5, dpi=300, compression = 'lzw', path = "image")
 
```
```{r remove graph DF}
rm(list = ls(pattern = "GRAPH_"))
```


# YEARLY COMPARISON

## Load Data Frame into R

Combine PPSFINALbyABX from previous year to current year
```{r combine PPSbyABX sheet}
#load available prevalence_analysis.xlsx
existing_PPSbyABX <- read_excel(paste0("excel/FINALPPSbyABX_", second_latest_year, ".xlsx"))

#join existing + new prevalence analysis into one spreadsheet
combined_ABX_data <- bind_rows(existing_PPSbyABX, ABX_data)

#save to excel sheet
write_xlsx(combined_ABX_data, paste0("excel/FINALPPSbyABX_", latest_year, ".xlsx"))

rm(existing_PPSbyABX)
```


```{r wrangle all df}
#mutate factor
combined_prev_analysis <-
combined_prev_analysis %>%
  mutate(Abx_prescribed = factor(Abx_prescribed, levels = c("yes", "no"))) #change order of Yes & No

 #mutate factor
combined_ABX_data <-
  combined_ABX_data %>%
  mutate(INDICATION_DOCUMENTED = factor(INDICATION_DOCUMENTED, levels = c("yes", "no"))) %>% #change order of Yes & No
  mutate(Empirical = case_when(
    CATEGORY == "empirical therapy" ~ "yes",
    TRUE ~ "no"  # For all other cases
  )) %>%
  mutate(Empirical = factor(Empirical, levels = c("yes", "no")))#change order of Yes & No

```

### Comparison antibiotics

```{r antibiotic latest year vs prev year}

COMPARE_df <- ABX_data %>%
  count(ABX_NAME, sort = TRUE) %>%
  slice_head(n = 10) %>%
  mutate(number = row_number()) %>%
  select(-n)

COMPARE_ABX_COMPARE <- combined_ABX_data %>%
  select(Year, ABX_NAME) %>%
  mutate(across(where(is.character),tolower)) %>%
  filter(Year %in% sort(unique(Year), decreasing = TRUE)[1:2]) %>%
  group_by(Year) %>%
  count(ABX_NAME, sort = TRUE) %>% 
  mutate(percentage =n/sum(n)) %>%
  mutate(percentage =round(percentage, 3)) %>%
  mutate(percentage =ifelse(Year == latest_year,percentage, -1*percentage)) %>%
  mutate(Year = factor(Year, levels = c(latest_year, second_latest_year))) %>%
  filter(ABX_NAME %in% COMPARE_df$ABX_NAME)

COMPARE_joined_abx_compare <- left_join(COMPARE_ABX_COMPARE, COMPARE_df, by = "ABX_NAME")

COMPARE_joined_abx_compare %>%
  ggplot(aes(x = reorder(ABX_NAME, -number), y = percentage, fill = Year)) + 
  geom_col(color = "black") + 
  geom_hline(yintercept = 0) +
  coord_flip() +
  geom_text(aes(label = paste0(n, '(', abs(percentage*100),'%)')), position = position_stack(vjust = 0.5), size = 2.5, check_overlap = TRUE) +
  labs(title = glue("Top ABX ({latest_year} vs {second_latest_year})"),
       x = "",
       y = "",
       fill = "Year") +
  scale_y_continuous(labels = function(x) percent(abs(x))) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        panel.background = element_rect(fill = "white"),
        axis.text = element_text(size = 7),
        legend.text = element_text(size = 7),
        legend.title = element_text(size = 7),
        axis.text.y = element_text(size = 12, face = "bold"))

ggsave("TOTALABXbyYEAR.tiff", units="in", width=10, height=5, dpi=300, compression = 'lzw', path = "image")
```

### Comparison prescriber

```{r discipline by year}

disc_df1 <- ABX_data %>%
  count(DISCIPLINE, sort = TRUE) %>%
  slice_head(n = 9) %>%
  mutate(number = row_number()) %>% 
  rename(Discipline = DISCIPLINE) %>%
  select(-n)

disc_COMPARE <-combined_ABX_data %>%
  select(Year, DISCIPLINE) %>%
  rename(Discipline = DISCIPLINE) %>% 
  filter(Year %in% sort(unique(Year), decreasing = TRUE)[1:2]) %>%
  group_by(Year) %>%
  count(Discipline, sort = TRUE) %>% 
  mutate(percentage =n/sum(n)) %>%
  mutate(percentage =round(percentage, 3)) %>%
  mutate(percentage =ifelse(Year == latest_year,percentage, -1*percentage)) %>%
  mutate(Year = factor(Year))  %>%
  filter(Discipline %in% disc_df1$Discipline)

disc_joined_prescriber <- left_join(disc_COMPARE, disc_df1, by = "Discipline")

disc_joined_prescriber %>% 
  ggplot(aes(x = reorder(Discipline, -number), y = percentage, fill = Year)) + 
  geom_col(color = "black") + 
  geom_hline(yintercept = 0) +
  coord_flip() +
  geom_text(aes(label = paste0(n, '(', abs(percentage*100),'%)')), position = position_stack(vjust = 0.5), size = 2.5, check_overlap = TRUE) +
  labs(title = glue("Top Prescriber ({latest_year} vs {second_latest_year})"),
       x = "",
       y = "",
       fill = "Year") +
  scale_y_continuous(labels = function(x) percent(abs(x))) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        panel.background = element_rect(fill = "white"),
        axis.text = element_text(size = 7),
        legend.text = element_text(size = 7),
        legend.title = element_text(size = 7),
        axis.text.y = element_text(size = 12, face = "bold"))
ggsave("TOPPRESCRIBERbyYEAR.tiff", units="in", width=10, height=5, dpi=300, compression = 'lzw', path = "image") 
```

# DATA ANALYSIS/INFERENTIAL STATISTICS - compare with previous year

## wrangling

```{r Discipline}

disc_med <-
  combined_ABX_data %>%
  select(Year, DISCIPLINE) %>%
  rename(Discipline = DISCIPLINE) %>%
  mutate(Discp = ifelse(Discipline == "General Medical", "Medical", "Non-Medical")) %>%
  select(Year, Discp) %>%
  filter(Year %in% sort(unique(Year), decreasing = TRUE)[1:2])

disc_ortho <-
  combined_ABX_data %>%
  select(Year, DISCIPLINE) %>%
  rename(Discipline = DISCIPLINE) %>%
  mutate(Discp = ifelse(Discipline == "Orthopaedic", "Ortho", "Non-ortho")) %>%
  select(Year, Discp) %>%
  filter(Year %in% sort(unique(Year), decreasing = TRUE)[1:2])

disc_Paeds <-
  combined_ABX_data %>%
  select(Year, DISCIPLINE) %>%
  rename(Discipline = DISCIPLINE) %>%
  mutate(Discp = ifelse(Discipline == "Paediatric", "Paeds", "Non-Paeds")) %>%
  select(Year, Discp) %>%
  filter(Year %in% sort(unique(Year), decreasing = TRUE)[1:2])
 
disc_OnG <-
  combined_ABX_data %>%
  select(Year, DISCIPLINE) %>%
  rename(Discipline = DISCIPLINE) %>%
  mutate(Discp = ifelse(Discipline == "O&G", "O&G", "Non-O&G")) %>%
  select(Year, Discp)%>%
  filter(Year %in% sort(unique(Year), decreasing = TRUE)[1:2])

disc_icu <-
  combined_ABX_data %>%
  select(Year, DISCIPLINE) %>%
  rename(Discipline = DISCIPLINE) %>%
  mutate(Discp = ifelse(Discipline == "Intensive Care Unit", "ICU", "Non-ICU")) %>%
  select(Year, Discp) %>%
  filter(Year %in% sort(unique(Year), decreasing = TRUE)[1:2])

disc_ID <-
  combined_ABX_data %>%
  select(Year, DISCIPLINE) %>%
  rename(Discipline = DISCIPLINE) %>%
  mutate(Discp = ifelse(Discipline == "Infectious Disease", "ID", "Non-ID")) %>%
  select(Year, Discp) %>%
  filter(Year %in% sort(unique(Year), decreasing = TRUE)[1:2])

disc_neonate <-
  combined_ABX_data %>%
  select(Year, DISCIPLINE) %>%
  rename(Discipline = DISCIPLINE) %>%
  mutate(Discp = ifelse(Discipline == "Neonates/NICU", "Neonates", "Non-Neonates")) %>%
  select(Year, Discp) %>%
  filter(Year %in% sort(unique(Year), decreasing = TRUE)[1:2])

disc_gensurg <-
  combined_ABX_data %>%
  select(Year, DISCIPLINE) %>%
  rename(Discipline = DISCIPLINE) %>%
  mutate(Discp = ifelse(Discipline == "General Surgical", "Gen-Surgical", "Non Gen-Surg")) %>%
  select(Year, Discp) %>%
  filter(Year %in% sort(unique(Year), decreasing = TRUE)[1:2])

disc_plastic <-
  combined_ABX_data %>%
  select(Year, DISCIPLINE) %>%
  rename(Discipline = DISCIPLINE) %>%
  mutate(Discp = ifelse(Discipline == "Plastic & Reconstructive Surgery", "Plastic", "Non plastic")) %>%
  select(Year, Discp) %>%
  filter(Year %in% sort(unique(Year), decreasing = TRUE)[1:2])
```

## Generate tbl_summary

```{r Comparison by Discipline from prev year using tbl_summary}

disc_med %>%
tbl_summary(by = Year, 
              type = list(Discp ~ "categorical"),
              label = Discp ~ "Discipline") %>%
  modify_header(label ~ " ") %>%
  modify_spanning_header(c("stat_1", "stat_2") ~ "**Year**") %>%
  bold_labels() %>%
  add_p()

disc_ortho %>%
tbl_summary(by = Year, 
              type = list(Discp ~ "categorical"),
              label = Discp ~ "Discipline") %>%
  modify_header(label ~ " ") %>%
  modify_spanning_header(c("stat_1", "stat_2") ~ "**Year**") %>%
  bold_labels() %>%
  add_p()

disc_Paeds %>%
tbl_summary(by = Year, 
              type = list(Discp ~ "categorical"),
              label = Discp ~ "Discipline") %>%
  modify_header(label ~ " ") %>%
  modify_spanning_header(c("stat_1", "stat_2") ~ "**Year**") %>%
  bold_labels() %>%
  add_p()

disc_OnG %>%
tbl_summary(by = Year, 
              type = list(Discp ~ "categorical"),
              label = Discp ~ "Discipline") %>%
  modify_header(label ~ " ") %>%
  modify_spanning_header(c("stat_1", "stat_2") ~ "**Year**") %>%
  bold_labels() %>%
  add_p()

disc_icu %>%
tbl_summary(by = Year, 
              type = list(Discp ~ "categorical"),
              label = Discp ~ "Discipline") %>%
  modify_header(label ~ " ") %>%
  modify_spanning_header(c("stat_1", "stat_2") ~ "**Year**") %>%
  bold_labels() %>%
  add_p()

disc_ID %>%
tbl_summary(by = Year, 
              type = list(Discp ~ "categorical"),
              label = Discp ~ "Discipline") %>%
  modify_header(label ~ " ") %>%
  modify_spanning_header(c("stat_1", "stat_2") ~ "**Year**") %>%
  bold_labels() %>%
  add_p()

disc_neonate %>%
tbl_summary(by = Year, 
              type = list(Discp ~ "categorical"),
              label = Discp ~ "Discipline") %>%
  modify_header(label ~ " ") %>%
  modify_spanning_header(c("stat_1", "stat_2") ~ "**Year**") %>%
  bold_labels() %>%
  add_p()

disc_gensurg %>%
tbl_summary(by = Year, 
              type = list(Discp ~ "categorical"),
              label = Discp ~ "Discipline") %>%
  modify_header(label ~ " ") %>%
  modify_spanning_header(c("stat_1", "stat_2") ~ "**Year**") %>%
  bold_labels() %>%
  add_p()

disc_plastic %>%
tbl_summary(by = Year, 
              type = list(Discp ~ "categorical"),
              label = Discp ~ "Discipline") %>%
  modify_header(label ~ " ") %>%
  modify_spanning_header(c("stat_1", "stat_2") ~ "**Year**") %>%
  bold_labels() %>%
  add_p()
```

## Comparison Table & Cross-Tab by year

```{r Comparison Table & Cross-Tab}

TABLE_PREVALENCE <- combined_prev_analysis %>%
  filter(Year %in% sort(unique(Year), decreasing = TRUE)[1:2]) %>%
  select(Year, Abx_prescribed) %>% 
  tbl_summary(by = Year, 
              type = all_dichotomous() ~ "categorical",
              label = Abx_prescribed ~ "Patients on Antibiotics") %>%
  modify_header(label ~ " ") %>%
  modify_spanning_header(c("stat_1", "stat_2") ~ "**Year**") %>%
  bold_labels() %>%
  add_p()

TABLE_INDDOCUMENTED <- combined_ABX_data %>% 
  filter(Year %in% sort(unique(Year), decreasing = TRUE)[1:2]) %>%
  select(Year, INDICATION_DOCUMENTED) %>%
  tbl_summary(by = Year, 
              type = all_dichotomous() ~ "categorical",
              label = INDICATION_DOCUMENTED ~ "Indication Documented") %>%
  modify_header(label ~ " ") %>%
  modify_spanning_header(c("stat_1", "stat_2") ~ "**Year**") %>%
  bold_labels() %>%
  add_p()

TABLE_BYYEARINDDOC <- combined_ABX_data %>% 
  filter(Year %in% sort(unique(Year), decreasing = TRUE)[1:2]) %>%
  select(Year, INDICATION_DOCUMENTED) %>%
  tbl_cross(row = Year, col = INDICATION_DOCUMENTED, percent = "cell") %>%
  modify_spanning_header(c("stat_1", "stat_2") ~ "**Indication Documentation**") %>%
  add_p() %>%
  bold_labels()

TABLE_EMPIRICAL <- combined_ABX_data %>% 
  filter(Year %in% sort(unique(Year), decreasing = TRUE)[1:2]) %>%
  select(Year, Empirical) %>%
  tbl_cross(row = Year, col = Empirical, percent = "cell") %>%
  modify_spanning_header(c("stat_1", "stat_2") ~ "**Empirical**") %>%
  add_p() %>%
  bold_labels()

TABLE_PREVALENCE
TABLE_INDDOCUMENTED
TABLE_BYYEARINDDOC
TABLE_EMPIRICAL

# List of tables
table_list <- c("TABLE_PREVALENCE", "TABLE_INDDOCUMENTED", "TABLE_BYYEARINDDOC", "TABLE_EMPIRICAL")

# Function to save each table
save_table_as_docx <- function(i) {
  table_obj <- get(i) %>%
    as_flex_table()
  
  file_path <- paste0("table/", tolower(i), ".docx")
  flextable::save_as_docx(table_obj, path = file_path)
  
  message("✅ Saved: ", file_path)
}

# Apply function to all tables
lapply(table_list, save_table_as_docx)

```

```{r remove df2}
rm(list = ls(pattern = "disc_"))
rm(list = ls(pattern = "COMPARE_"))
rm(list = ls(pattern = "TABLE"))
```

# THE END
